\documentclass{article}

\usepackage{amsmath,amsthm}


\newtheorem{ass}{Assumption}

\begin{document}
\section{Tests with Estimated Nuisance Parameters}
\label{sec:testWithPihat}

\begin{ass}
  \label{ass:C}
  \begin{enumerate}
  \item\label{ass:C:First} Here is the first condition.
  \item\label{ass:C:Second} Here is another.
  \end{enumerate}
\end{ass}

\begin{equation*}
  2x +3
\end{equation*}

\begin{itemize}
\item \label{it:new} blabla
\end{itemize}

\ref{it:new}

\begin{multline}
  \label{mult}
  3x + 4
\end{multline}

This file contains several bibliography entries but not all of them are
explicitly cited. Actually, only explicit references to \cite{mpitb} and
\cite{lambertonlapeyre} can be found.

\begin{thebibliography}{X}
\bibitem{mpitb}
  {Javier Fern\'andez Baldomero and Mancia Anguita}.
  \newblock Mpi toolbox (mpitb).
  \newblock Technical report, Depto. de Arquitectura y Tecnolog\'{\i}a de
  Computadores, ETSI Inform\'atica, Universidad de Granada, 2000--2008.
  \newblock \verb!http://atc.ugr.es/javier-bin/mpitb!.

\bibitem{lambertonlapeyre}
  D.~Lamberton and B.~Lapeyre.
  \newblock {\em Introduction to stochastic calculus applied to finance}.
  \newblock Chapman \& Hall/CRC Financial Mathematics Series. Chapman \&
  Hall/CRC, Boca Raton, FL, second edition, 2008.

\bibitem{premia}
  {MathFi Research Group}.
  \newblock A platform for pricing financial derivatives.
  \newblock Technical report, Inria and Universit\'e Paris Est, CERMICS, \'Ecole de
  Ponts, 2008.
  \newblock \verb!http://www-rocq.inria.fr/mathfi/Premia!.
\end{thebibliography}
\end{document}

